---
title: "Censoring Exploration"
author: "Sara Stoudt"
date: "2/16/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning= F, message = F}
library(dplyr)
library(ggplot2)

setwd("~/Desktop/kidz-bop-data/")
badWordSummary = read.csv("data/censoring/censoringTimes.csv", stringsAsFactors = F)
fullData = read.csv("data/censoring/fullDataSet.csv", stringsAsFactors = F)

load(file="data/2020-02-02/ogLyricsFullPlain.RData") ## ogLyricsFull
load(file="data/2020-02-02/kbLyrics.RData") ## kbLyrics

kb40_gender <- read.csv("data/2020-02-02/originalArtists_gender-KB_40.csv", stringsAsFactors = F)
```

## What is being censored by category?

```{r}
fullData %>% group_by(category) %>% summarise(countCensored=sum(isCensored), count = sum(isPresent)) %>% mutate(prop = countCensored/count)

```

## Consistency of Censoring

```{r}
## took a while to censor
badWordSummary$bad_word[which(badWordSummary$firstCensored>badWordSummary$firstAppear)]
## confirms livin la vida loca

## sometimes not censored
badWordSummary$bad_word[which(badWordSummary$numPresent>badWordSummary$numCensored)]
## some of these seem like they should always be censored

## always censored
badWordSummary$bad_word[which(badWordSummary$numPresent==badWordSummary$numCensored)]
## women?
```

## Looking into consistency 

```{r}
fullData %>% filter(isPresent & bad_word =="nigga")

#kbLyrics[[474]] %>% View()
#kbLyrics[[536]] %>% View()

fullData %>% filter(isPresent & bad_word =="dammit")

```

Kidz Bop words do have the word in it on Genius:

https://genius.com/Kidz-bop-kids-suit-and-tie-lyrics

https://genius.com/Kidz-bop-kids-u-dont-have-to-call-lyrics

https://genius.com/Kidz-bop-kids-i-cry-lyrics

```{r}
fullData %>% filter(isPresent & bad_word =="women")

#kbLyrics[[276]] %>% View()
## intro with "women" not present, does keep god in though fyi

#kbLyrics[[140]] %>% View()
#ogLyricsFull[[133]] %>% View()
## Women steady comin' after me	
## Men steady comin' after you	

## switched to girls and boys
```

Intro with "women" not present in "Jenny From the Block." Kidz Bop does keep "god" in though FYI.

In Akon's song: "Women steady comin' after me," "Men steady comin' after you." Kidz Bop changes this to "girls" and "boys"

So it looks like we have some false negatives, not sure what to do about that.

## Censoring over time

```{r}
overTime = fullData %>% group_by(kb_release_year) %>% summarise(countCensored=sum(isCensored), count = sum(isPresent)) %>% mutate(prop = countCensored/count)

ggplot(overTime, aes(kb_release_year,count))+geom_point()+geom_line()+ylab("existence of words")
# picking songs that don't need as much censoring?

ggplot(overTime, aes(kb_release_year,prop))+geom_point()+geom_line()+ylab("censored / present")
# proportion of potentially problematic words being removed over time
```

Well that is striking.

## Time Trends Per Category

```{r,fig.height=12, fig.width=12}
overTime = fullData %>% group_by(kb_release_year,category) %>% summarise(countCensored=sum(isCensored), count = sum(isPresent)) %>% mutate(prop = countCensored/count)


ggplot(overTime, aes(kb_release_year,count))+geom_point()+geom_line()+facet_wrap(~category)+ylab("existence of words")

ggplot(overTime, aes(kb_release_year,prop))+geom_point()+geom_line()+facet_wrap(~category)+ylab("censored / present")



```

Slight increase in existence of alcohol & drugs and profanity over time. 

Censorship of alcohol and drugs, sexual groups increasing over time. 

## Kidz Bop 40 Gender

```{r}
kb40 = fullData %>% filter(kb_release_year == max(fullData$kb_release_year)) 
kb40_gender$song = tolower(kb40_gender$song)

test = merge(kb40, kb40_gender, by.x="kb_song_name", by.y="song",all.y=T, all.x=F) 

test %>% filter(!is.na(og_idx)) %>% group_by(gender) %>% summarise(countCensored = sum(isCensored), count = sum(isPresent))

toP = test %>% filter(!is.na(og_idx)) %>% group_by(gender,category) %>% summarise(countCensored = sum(isCensored), count = sum(isPresent)) %>% mutate(prop = countCensored/count)


ggplot(toP, aes(gender, prop))+geom_bar(stat = "identity") +facet_wrap(~category)


```

A little too sparse to see anything.